\bf Faster Neural Machine Translation Inference

### 2018-02-06 fast-beam/fast-beam.tex
fast beam paper

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		& Baseline	& Fused \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 1}}	\\ \hline	
Multiplication 	& 25.62 	& 26.47 (+3.3\%) \\ \hline
Add bias 	& 4.98		&  \\ 
Softmax 	& 12.81		& 7.94 (-76.9\%)\\
Beam search	& 16.64		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 5}}	\\ \hline	
Multiplication 	& 112.9 	& 115.04 (+1.9\%) \\ \hline
Add bias 	& 23.66		&  \\ 
Softmax 	& 56.61		& 67.58 (-56.5\%)\\
Beam search	& 75.12		&  \\ \hline
\end{tabular}
\end{center}
\caption{Time taken in sec (Europarl)}
\label{tab:fused-breakdown}
\end{table}

>>>>

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		& Baseline	& Fused \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 1}}	\\ \hline	
Multiplication 	& 25.62 	& 26.47 (+3.3\%) \\ \hline
Add bias 	& 4.98		&  \\ 
Softmax 	& 12.81		& 7.94 (-76.9\%)\\
Beam search	& 16.64		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 5}}	\\ \hline	
Multiplication 	& 112.9 	& 115.04 (+1.9\%) \\ \hline
Add bias 	& 23.66		&  \\ 
Softmax 	& 56.61		& 67.58 (-56.5\%)\\
Beam search	& 75.12		&  \\ \hline
\end{tabular}
\end{center}
\caption{Time taken in sec (Europarl)}
\label{tab:fused-breakdown-europarl}
\end{table}

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		& Baseline	& Fused \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 1}}	\\ \hline	
Multiplication 	& 21.47 	& 21.94 (+2.2\%) \\ \hline
Add bias 	& 33.59		&  \\ 
Softmax 	& 8.83		& 5.70 (-89.9\%)\\
Beam search	& 13.91		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 5}}	\\ \hline	
Multiplication 	& 79.66 	& 80.01 (+4.4\%) \\ \hline
Add bias 	& 14.95		&  \\ 
Softmax 	& 36.86		& 42.91 (-64.4\%)\\
Beam search	& 68.80		&  \\ \hline
\end{tabular}
\end{center}
\caption{Time taken in sec (OpenSubtitles)}
\label{tab:fused-breakdown-opensubtitles}
\end{table}
